Learning and comparing functional connectomes across subjects

### 2013-02-24 paper.tex
Address more points

Reviewing methodological options to learn and compare connectomes
highlights that there is currently no unique solution, but a spectrum of
related methods and analytical strategies. More empirical results are
required to guide the choices. However this diversity is probably
unavoidable: a diffuse disease like schizophrenia will not lead to the
same connectome modifications as a focal lesion. In statistical learning,
``no free lunch'' theorems \cite{wolpert1996} tell us that no strategy
can perform uniformly better in all situations. In practice, the key to a
successful analysis is to understand well the assumptions and
interpretation of each option, in order to match the method to the
question.

% Acknowledgments: Bertrand, Andreas, NiConnect

>>>>

Reviewing methodological options to learn and compare connectomes
highlights that there is currently no unique solution, but a spectrum of
related methods and analytical strategies. More empirical results are
required to guide the choices. However this diversity is probably
unavoidable: a diffuse disease like schizophrenia will not lead to the
same connectome modifications as a focal lesion. In statistical learning,
``no free lunch'' theorems \cite{wolpert1996} tell us that no strategy
can perform uniformly better in all situations. In practice, the key to a
successful analysis is to understand well the assumptions and
interpretation of each option, in order to match the method to the
question. Similarly, the idealized notion of an unique \emph{functional
connectome} to describe connections in brain function is probably an
utopia, and various connectomes should be considered in different
settings, such as the study of varying phenotypic conditions, or that of
on-going activity versus activity related to specific tasks.

\subsection*{Acknowledgments}

GV acknowledges funding from the NiConnect grant, as well as many
insightful discussions with Andreas Kleinschmidt on on-going activity and
Bertrand Thirion on statistical data processing.
